---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tppr)
```

```{r, include = FALSE}
# Prepare data for the analysis
# Read raw data
raw <- tppr::read_data(type = "live", source = "download")

# Clean raw data
processed <- tppr::clean_data(raw)

# Check current checkpoint
current_checkpoint <- tppr::tell_checkpoint(df = processed)

# Calculate cumulative success
cumulative <- tppr::cumulative_success(df = processed)
cumulative_bayes <- tppr::cumulative_bayes_factor(df = cumulative)

# Run robustness analysis
total_n <- nrow(processed)
success <- sum(as.logical(processed$sides_match), na.rm = T)
  
robustness_bayes <- tppr::robustness_bf_analysis(success = success, total_n = total_n)

# Run exploratory analysis
exploratory <- tppr::analysis_exploratory(df = processed)

# Run descriptive analysis
descriptive <- tppr::sample_descriptives_current(processed_data = processed)
```

# transparent-psi-results

<!-- badges: start -->
<!-- badges: end -->

This repository contains the data collected for the [Transparent Psi Project](https://osf.io/jk2zf/). This README contains the results calculated from the currently available data. The document was last updated at `r Sys.Date()`.

```{r, echo = FALSE, results = 'asis'}
tppr::text_helper_warning(current_checkpoint$next_checkpoint)
```

# Summary of the results

```{r, echo = FALSE, results = 'asis'}
tppr::text_helper_current_general(descriptive, robustness_bayes)
```

# Main Confirmatory Analysis results

```{r, echo = FALSE, warning = FALSE}
tppr::plot_confirmatory(cumulative_bayes, animated = FALSE)
```

# Result of the Bayesian Parameter Estimation Robustness Analysis

```{r, echo = FALSE}
tppr::plot_robustness(posterior_density = robustness_bayes$posterior_density,
                      hdi_mode = robustness_bayes$hdi_mode,
                      hdi_l = robustness_bayes$hdi_l,
                      hdi_u = robustness_bayes$hdi_u,
                      include_nhst = FALSE)
```

# Histogram overlay of the expected and observed distribution of successful guess rate

```{r, echo = FALSE}
tppr::plot_exploratory(success_rates_theoretical_prop = exploratory$success_rates_theoretical_prop,
                       success_rates_empirical_prop = exploratory$success_rates_empirical_prop,
                       possible_success_rates = exploratory$possible_success_rates)
```
